Capstone Movielens Report

### 2025-01-31 reports/capstone-movielens-report.Rmd
First draft version of citing and bibliography implementation.

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: [references.bib]
#link-citations: true
output:
  html_document: 
    fig_caption: true
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Alphabetic Style}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=TRUE}
library(RefManageR)
bib <- ReadBib(system.file("Bib", "references.bib", 
                           package = "RefManageR"), check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
knitr::opts_chunk$set(echo = TRUE)
```

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the `Netflix Grand Prize Challenge` requirements`r AutoCite(bib, "NYT1MNP")`, we will evaluate the RMSE score`r AutoCite(bib, "IDS2_23-2")`:

Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563`r AutoCite(bib, "BigChaosSln")`).

@@

## Refs

[Rafael A. Irizarry. Introduction to Data Science, Part II](https://rafalab.dfci.harvard.edu/dsbook-part-2/)

1.23.2 [Section 23.2: Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function)

[Töscher, A., Jahrer, M., & Bell, R. M. (2009). The BigChaos Solution to the Netflix Grand Prize](https://www.asc.ohio-state.edu/statistics/statgen/joul_aut2009/BigChaos.pdf)

[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)]

>>>>

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: references.bib
#csl: bit-numerical-mathematics.csl 
output:
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
    citation_package: biblatex

  html_document: 
    fig_caption: true
# hyperrefoptions:
#   - backref
colorlinks: true
linkcolor: red
citecolor: blue
header-includes:
    - \usepackage{hyperref}
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Numeric Style}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::knitr}
---

```{r setup, include=TRUE, echo = FALSE}
library(RefManageR)
bib <- ReadBib("references.bib", check = FALSE)
BibOptions(check.entries = FALSE,
           hyperlink = "to.bib",
           bib.style = "numeric", 
           style = "markdown", 
           cite.style = 'numeric')

citeB <- function(citeKey){
  Cite(bib, citeKey, .opts = list(super = FALSE))
}

knitr::opts_chunk$set(echo = TRUE)

# \usepackage[utf8]{inputenc}
# \usepackage[english]{babel}
# \usepackage{biblatex}

```

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the _Netflix Grand Prize Contest_`r # \cite{knuthwebsite}` `r citeB("NYT1MNP")`  requirements, we will evaluate the RMSE score defined as`r citeB("IDS2_23-2")`:

$$
\mbox{RMSE} = \sqrt{\frac{1}{N} \sum_{i,j}^{N} (y_{i,j} - \hat{y}_{i,j})^2}
$$

with $N$ being the number of user/movie combinations for which we make predictions and the sum occurring over all these combinations.

Our goal is to achieve a value of less than 0.86490 (compare with the _Netflix Grand Prize_ requirement: of at least 0.8563`r citeB("BigChaosSln")`).

### Dataset

@@

**References**

```{r results = "asis", echo = FALSE}
# \addcontentsline{toc}{section}{References} 
#\printbibliography[title={Whole bibliography}]
# 
# \color{black}
# \bibliography{references}
# \bibliographystyle{mla-good}
#\bibliographystyle{mla-good}
#\bibliographystyle{is-unsrt}
#\bibliographystyle{is-plain}
#\bibliographystyle{is-abbrv}
#\bibliographystyle{apalike}

PrintBibliography(bib,
                  .opts = list(check.entries = FALSE,
                               hyperlink = "to.bib",
                               first.inits = FALSE,
                               bib.style = "numeric",
                               style = "markdown",
                               cite.style = 'numeric'))

```
